---
title: "Business Intelligence Project"
author: "Alex MWai Muthee"
date: "27/11/2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | 131123 |
| **Student Name**                             | Alex Mwai Muthee |
| **BBIT 4.2 Group**                           | B |
| **BI Project Group Name/ID (if applicable)** | ... |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset
startup = read.csv("data/startupdata.csv")

### Source:

The dataset that was used can be downloaded here: https://www.kaggle.com/datasets/manishkc06/startup-success-prediction

### Reference:

*\<Cite the dataset here using APA\>\
KC, M. (2018). Startup Success Prediction [Data set]. Kaggle. Retrieved from https://www.kaggle.com/datasets/manishkc06/startup-success-prediction

```{r Dataset Loader}
library(readr)
##Other required libraries
library(data.table)
library(ggplot2)
library(ggridges)
library(grid)
library(gridExtra)
library(GGally)
library(dplyr)
library(ggplot2)
library(tidyr)
library(reshape2)
library(cluster)
library(class)
library(caret)
library(rpart)
library(plumber)
library(randomForest)
library(ggcorrplot)

# Provide the executable R code inside the various code chunks as guided by the lab work.
startup = read.csv("../data/startupdata.csv")

##View the data

View(startup)
names(startup)
head(startup)
class(startup)
summary(startup)
str(startup)

table(startup$state_code)
table(startup$category_code)
table(startup$status)
table(startup$state_code, startup$status)

## Descriptive statistics
### Mean
mean(startup$funding_total_usd, na.rm = TRUE)

### Median
median(startup$funding_total_usd, na.rm = TRUE)


### Range
range(startup$funding_total_usd, na.rm = TRUE)

### Quartiles
quantile(startup$funding_total_usd, na.rm = TRUE)

### Variance
var(startup$funding_total_usd, na.rm = TRUE)

### Standard Deviation
sd(startup$funding_total_usd, na.rm = TRUE)


### Correlation
cor(startup$age_first_funding_year, startup$funding_total_usd, use = "complete.obs")

```