---
title: "Business Intelligence Project"
author: "Alex Mwai Muthee"
date: "27/11/2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |     |
|----------------------------------------------|-----|
| **Student ID Number**                        | 131123 |
| **Student Name**                             | Alex Mwai Muthee |
| **BBIT 4.2 Group**                           | B |
| **BI Project Group Name/ID (if applicable)** | ... |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset
startup = read.csv("data/startupdata.csv")

### Source:

The dataset that was used can be downloaded here: https://www.kaggle.com/datasets/manishkc06/startup-success-prediction

### Reference:

*\<Cite the dataset here using APA\>\
KC, M. (2018). Startup Success Prediction [Data set]. Kaggle. Retrieved from https://www.kaggle.com/datasets/manishkc06/startup-success-prediction

```{r Dataset Loader}
#Required libraries
library(plumber)
library(caret)

# Load the model
# I chose the desicion tree because it is the most accurate
tree_model <- readRDS("../models/tree_model.rds")


category_code_levels <- c("advertising", "analytics", "automotive", "biotech", "cleantech", "consulting",
                          "ecommerce", "education", "enterprise", "fashion", "finance", "games_video",
                          "hardware", "health", "hospitality", "manufacturing", "medical", "messaging",
                          "mobile", "music", "network_hosting", "news", "other", "photo_video",
                          "public_relations", "real_estate", "search", "security", "semiconductor",
                          "social", "software", "sports", "transportation", "travel", "web")

state_levels <- c("California", "Massachusetts", "New York", "Other states", "Texas", "Unknow")

industry_levels <- c("Advertising", "Biotech", "Consulting", "Ecommerce", "Enterprise", "Mobile",
                     "Other Category", "Software", "Video Games", "Web")

#* @apiTitle Startup Prediction Model API
#* @apiDescription Predict startup success

#* @param funding_total_usd Total funding in USD
#* @param funding_rounds Number of funding rounds
#* @param milestones Number of milestones
#* @param category_code Category code of the startup
#* @param state State where the startup is located
#* @param industry Industry of the startup
#* @get /predict_startup
function(funding_total_usd, funding_rounds, milestones, category_code, state, industry) {
  to_be_predicted <- data.frame(
    funding_total_usd = as.numeric(funding_total_usd),
    funding_rounds = as.numeric(funding_rounds),
    milestones = as.numeric(milestones),
    category_code = factor(category_code, levels = category_code_levels ),
    state = factor(state, levels = state_levels ),
    industry = factor(industry, levels = industry_levels)
  )
  

  predictions_tree <- predict(tree_model, to_be_predicted, type = "class")
  return(predictions_tree)
}





```